Plot densities for simulation studies

### 2016-12-20 analysis/plot_egdens.Rmd
Successfully re-knit plot_egdens.Rmd using ashr 2.0.4.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

```{r}
library("ashr")
library("ggplot2")
library("dplyr")
library("dscr")
load("../output/dsc-shrink-files/res.RData")
PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","big-normal","bimodal")
PLOTNAMES = PLOTSCENARIOS
#PLOTFILE = "../paper/figures/scenarios_density.pdf"

df=data.frame()

for(i in PLOTSCENARIOS){
  s=dsc_shrink$scenarios[[i]]
  g=s$args$g
  x = seq(-6,6,length=100)
  y = as.numeric(dens(g,x))
  df = rbind(df,data.frame(x=x,y=y,scenario=i))
}

df$scenario = factor(df$scenario,levels=PLOTSCENARIOS)
levels(df$scenario)= PLOTNAMES
```

```{r scenario_density}
#pdf(PLOTFILE,height=3,width=9)
ggplot(df, aes(x=x,y=y)) + geom_line(size=1.2,linetype=1) + facet_grid(.~scenario) + ylab("density")
#dev.off()
```

>>>>

```{r chunk_options, include=FALSE}
library(ashr)
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

Load the results of the simulation experiments, and generate the density
data for all the simulation scenarios in a single data frame ("df").

```{r chunk_label}
load("../output/dsc-shrink-files/res.RData")
PLOTSCENARIOS = c("spiky","near-normal","flat-top","skew","bimodal")
PLOTNAMES     = PLOTSCENARIOS

df = data.frame()
for(i in PLOTSCENARIOS) {
  s  = dsc_shrink$scenarios[[i]]
  g  = s$args$g
  x  = seq(-6,6,length = 100)
  y  = as.numeric(dens(g,x))
  df = rbind(df,data.frame(x = x,y = y,scenario = i))
}

df$scenario         = factor(df$scenario,levels = PLOTSCENARIOS)
levels(df$scenario) = PLOTNAMES
```

Generate density plots using ggplot.

```{r scenario_density, dev='pdf',fig.height=3, fig.width=9, crop=TRUE}
ggplot(df,aes(x = x,y = y)) + 
  geom_line(size = 1.2,linetype = 1) + 
  facet_grid(.~scenario) + 
  ylab("density")
```
